\documentclass{article}
\usepackage{calc}
\usepackage[landscape] {geometry}
\usepackage{fullpage}
\pagestyle{empty}


\iffalse
Thanks to user1999 from stackexchange. 
http://tex.stackexchange.com/users/1999/user1999
\fi
\newlength{\remaining}
\newcommand{\titleline}[1]{%
\setlength{\remaining}{\textwidth-\widthof{\textsc{#1}}-2cm}
\noindent\underline{\textsc{#1}\hspace*{\remaining}}\par}




\begin{document}
\large

We're delighted that you're interested in becoming a member!  Here's how to do it:

\vfill

\begin{enumerate}

\item 

Just start showing up!  Open meetings are every Tuesday night starting
at 7:00 PM at the downtown space in the Sun Center, 101 SE 2nd place.

Gainesville Hackerspace is a community more
than a service organization.  Join the facebook group, mailing list,
meetup.. and just show up when things are happening.    

Introduce yourself on the mailing list, tell us what you're into.

\vfill
\item

Tell us a little bit about yourself.  Most of this information is
pretty self-explanatory.  We use a username for some internal systems;
if you're interested, you can also get mail forwarded from
\textit{username@skillhouse.org}.


\titleline{Name}
\titleline{Address }
\titleline{Phone number}
\titleline{Email}
\titleline{Username}
\titleline{Emergency contact}

\vfill
\item 

Once you've introduced yourself around, we'll vote on you in the
  next regular meeting (First open meeting of the month).  


\end{enumerate}

\vfill


Website: http://skillhouse.org \hfill  Mailing list: https://groups.google.com/d/forum/gainesville-hackerspace

Wiki: http://wiki.skillhouse.org/ \hfill  Facebook:  https://www.facebook.com/groups/39963409979/

Contact the board at \textit{ board@skillhouse.org }. \hfill Bylaws: http://static.skillhouse.org/bylaws.pdf

\end{document}

